\documentclass{resume} % Use the custom resume.cls style
\newcommand{\myitemsep}{\itemsep -0.6em}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Shuai Zhang}

\address{100 N Hearthstone Way, Chandler, AZ \\ \href{https://www.linkedin.com/in/shuaizhang39/}{resume.shuainium.com} \\ \href{mailto:hello@shuainium.com}{hello@shuainium.com} \\ (608) 421-0730}

\begin{document}

  \newcommand\LineShrinkBeforeItem{\vspace*{-1.5em}}

  %----------------------------------------------------------------------------------------
  %   EDUCATION SECTION
  %----------------------------------------------------------------------------------------

  \begin{rSection}{Education}

    {\bf Columbia University in the City of New York} \hfill {New York, NY}\\
    M.S. Computer Engineering  \hfill {Dec 2022}\\
    GPA: 3.5 / 4.0

    {\bf University of Wisconsin-Madison} \hfill {Madison, WI}\\
    B.S. Electrical Engineering \& B.S. Computer Science  \hfill {May 2021}\\
    GPA: 3.6 / 4.0

  \end{rSection}

  %----------------------------------------------------------------------------------------
  %   PROFESSIONAL EXPERIENCE
  %----------------------------------------------------------------------------------------

  \begin{rSection}{PROFESSIONAL EXPERIENCE}

    % Engineer
    \textbf{Arm, Inc.}                          \hfill Chandler, AZ         \\
    \emph{Verification Engineer}                             \hfill Apr 2024 - Present   \\
    \LineShrinkBeforeItem
    \begin{itemize} [leftmargin=1em]
      \myitemsep
      \item Owned verification of the Request Node (RNID) module in the Arm Coherent Mesh Network (CMN).
      \item Mentored and onboarded new team members in the RNID Val group, guiding them in verification methodology.
      \item Collaborated with the RTL team to develop detailed test plans for new CMN features.
      \item Coordinated with the top-level team to ensure regression stability and health.
      \item Developed unit-level UVM testbenches for RNID functional verification.
      \item Investigated and debugged regression failures in various components and environments.
      \item Defined and implemented functional and statistical coverage metrics, driving coverage closure.
    \end{itemize}

    % Graduate Verification Engineer
    \textbf{Arm, Inc.}                          \hfill Chandler, AZ         \\
    \emph{Graduate Verification Engineer}       \hfill Feb 2023 - Mar 2024  \\
    \LineShrinkBeforeItem
    \begin{itemize} [leftmargin=1em]
      \myitemsep
      \item Developing comprehensive verification strategies for Arm M-Class CPU memory system
      \item Constructing UVM testbenches for CPU memsys functional verification
      \item Developing and improving stimulus, test cases, testbench checkers and System Verilog assertions
      \item Debugging regression failures in simulation and formal and report bugs in the design under test
      \item Defining and implementing functional and statistical coverage and improving the testbench for coverage closure
    \end{itemize}

    % 2022 intern
    \textbf{Arm, Inc.}                          \hfill Chandler, AZ         \\
    \emph{CPU Verification Engineer Intern}     \hfill May 2022 - Aug 2022  \\
    \LineShrinkBeforeItem
    \begin{itemize} [leftmargin=1em]
      \myitemsep
      \item Migrated event/trace-based verification workflow from A class CPU to M class CPU
      \item Captured memory system RTL signal and compiled the signal into linked events
      \item Traced memory transaction events, and visualized them in an intuitive manner for easier debugging
    \end{itemize}

    % 2021 intern
    \textbf{Arm, Inc.}                          \hfill Chandler, AZ         \\
    \emph{CPU Verification Engineer Intern}     \hfill May 2021 - Aug 2021  \\
    \LineShrinkBeforeItem
    \begin{itemize} [leftmargin=1em]
      \myitemsep
      \item Optimized run-time performance of interrupt controller testbench
      \item Identified performance bottleneck and enhanced UVM testbench resource utilization
      \item Collaborated and Improved workflow efficiency by reducing testbench runtime overhead by 25\%
    \end{itemize}

  \end{rSection}

  %----------------------------------------------------------------------------------------
  %   RESEARCH EXPERIENCE
  %----------------------------------------------------------------------------------------

  \begin{rSection}{Research Experience}

    \textbf{University of Wisconsin - Madison: Photonics lab}   \hfill Apr 2019 - May 2021 \\
    \LineShrinkBeforeItem
    \begin{itemize} [leftmargin=1em]
      \myitemsep
      \item Contributed to a research group developing an ML-based magnetic levitation system.
      \item Collaborated on embedded system data acquisition and digital signal processing.
      \item Enhanced control system and circuitry, achieving a 10x reduction in response time overhead.
    \end{itemize}

  \end{rSection}

  \begin{rSection}{TECHNICAL SKILLS}

    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
      Programming Skills & Verilog / SystemVerilog, Python, C / C++, Java, MATLAB                    \\
      EDA Tools          & QuestaSim / Visualizer, QuestaFormal, Quartus, Vivado, DVT, Verdi         \\
      Computer Skills    & Linux, Git, VS Code, Jira, Jenkins                                        \\
    \end{tabular}\\

  \end{rSection}

\end{document}

% deprecated experiences

% \textbf{Columbia University: Creative Machines lab}         \hfill Jun 2020 - Dec 2020 \\
% \LineShrinkBeforeItem
% \begin{itemize} [leftmargin=1em]
%   \myitemsep
%   \item Contributed to an open-source research group focused on ultrasonic flaw detection systems.
%   \item Customized embedded system functions, including ADC/DAC, data flow, and data processing.
%   \item Optimized microcontroller code for improved run-time performance.
% \end{itemize}
